Spatial Reasoning and Data Displays

### 2015-06-26 Paper/InfoVis2015Revision/TestingVisualAptitude.Rnw
Updated appendix, regenerated pdfs, abstract typo fix

%% Abstract section.
\abstract{
Graphics convey numerical information very efficiently, but rely on a different set of mental processes than tabular displays. here, we present a study relating demographic characteristics and visual skills to perception of graphical lineups. We conclude that lineups are essentially a classification test in a visual domain, and that performance on the lineup protocol is associated with general aptitude, rather than specific tasks such as card rotation and spatial manipulation. We also examine the possibility that specific graphical tasks may be associated with certain visual skills and conclude that more research is necessary to understand which visual skills are required in order to understand certain plot types. 
} % end of abstract

@@

After each test or block of lineups, participants were given 1-2 minutes to rest and recover; the order of tests was designed to prevent fatigue on a single task. The duration of testing for each participant was approximately 1 hour.

>>>>

%% Abstract section.
\abstract{
Graphics convey numerical information very efficiently, but rely on a different set of mental processes than tabular displays. Here, we present a study relating demographic characteristics and visual skills to perception of graphical lineups. We conclude that lineups are essentially a classification test in a visual domain, and that performance on the lineup protocol is associated with general aptitude, rather than specific tasks such as card rotation and spatial manipulation. We also examine the possibility that specific graphical tasks may be associated with certain visual skills and conclude that more research is necessary to understand which visual skills are required in order to understand certain plot types. 
} % end of abstract

@@

After each test or block of lineups, participants were given 1-2 minutes to rest and recover; the order of tests was designed to prevent fatigue on a single task. The duration of testing for each participant was approximately 1 hour. All test documents (with redacted copyrighted material) are available as supplemental materials.
